Man's not hot, Man can never be hot

### 2018-01-16 article/ms.tex
intro edits

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[B. J. Norfolk et al.]{Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
Andrew R. Casey,$^{1,2}$
Ernie? Kemp? Karakas? Lattanzio? \newauthor
Schlaufman? others?
\\
% List of institutions
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
}

@@

Barium stars are chemically unusual red giants with an overabundance of carbon and heavy elements ($Z > 30$) relative to the Sun \citep{Bidelman1951}. \todo{Explain why this chemical signature is unusual: because this signature can really only be produced by TP-AGB stars, but we see barium stars that have not evolved to the AGB stars. Introduce extrinsic/intrinsic. Barium stars are considered to have been polluted by a binary TP-AGB star, or they are TP-AGB stars themselves.}

@@

About half of all heavy elements are produced by the slow neutron-capture process ($s$-process) inside asymptotic giant branch (AGB) stars \citep[e.g.][]{busso1999,travaglio2001,
herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
karakas12016}. 
\todo{This is very good, but the sentence needs splitting up: Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass, and will drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions.} The energy from each thermal pulse forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermally-driven convective zone. This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after every thermal pulse. 
The repeated downwash extensions of TDU cause enhancement of surface $^{12}$C abundance and of other heavy elements produced by the s-process \citep[e.g.,][]{busso2001}. The star contracts after \todo{PDU} and reignites the H-shell, producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.

Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metalicity decreases. The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr. In contrast, metal rich, young observable stars reaching the upper limit may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.

@@

According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}.

Barium stars currently have only been discovered in the disk and halo of the Galaxy according to \citet{gomez1997} and \citet{mennessier1997}. Both studies show the stellar populations of Barium stars can be seperated into two groups when divided according to luminosity, kinematic and spatial parameters. Barium stars populating the halo have already been investigated \citep[e.g.][]{junqueira2001,drake2008,pereira2009,allen2006} and their relationship with metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}. Additionally, \citet{pereira2011} concludes metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, demonstrating they do not belong to the bulge population. Furthermore, it is neccessary to establish known abundances of s-process elements in a greater sample of Barium stars to conclude the percentage population of said stars in the Galaxy, and compare with their theoratical birthrate \citep{han1995}

\todo{The red giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA\ and 4077\AA, respectively. (thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?). }

In this paper we analysis the \textit{Cannon} fitted LAMOST spectra \citep{ho2017} to obtain a sample set of s-process enriched Barium stars and investigate atmospheric parameters including, the distributions of temperature, surface gravity and metalicity. Additionally, the abundances of elements not produced in the s-process such as sodium and technetium (Na and Tc) are examined to determine  if the sample Barium stars share similar abundance to field giants with equal metallicities. Moreover, the stellar sample is cross matched with GAIA, producing (not sure exactly what gaia gave us) neccessary to determine the kinematics of our Barium samples.

In our research we analysed 273 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 273 canidates.

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[B. J. Norfolk et al.]{Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
Andrew R. Casey,$^{1,2}$
Ernie? Kemp? Karakas? Lattanzio? Ho?\newauthor
Schlaufman? others?
\\
% List of institutions
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
}

@@

Barium stars are red giants with an unusual overabundance of carbon and heavy elements ($Z > 30$) relative to the Sun \citep{Bidelman1951}. \todo{Explain why this chemical signature is unusual: because this signature can really only be produced by TP-AGB stars, but we see barium stars that have not evolved to the AGB stars. Introduce extrinsic/intrinsic. Barium stars are considered to have been polluted by a binary TP-AGB star, or they are TP-AGB stars themselves.}
For these reasons, the properties and occurrence rate of barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

@@

About half of all heavy elements are produced by the slow neutron-capture process (s-process) inside asymptotic giant branch (AGB) stars \citep[e.g.][]{busso1999,travaglio2001,
herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
karakas12016}. 
\todo{This is very good, but the sentence needs splitting up: Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass, and will drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions.} The energy from each thermal pulse forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermally-driven convective zone. This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after every thermal pulse. 
The repeated downwash extensions of TDU cause enhancement of surface $^{12}$C abundance and of other heavy elements produced by the s-process \citep[e.g.,][]{busso2001}. The star contracts after \todo{PDU} and reignites the H-shell, producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.

% Link AGB stars and barium stars.

According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small phase range as detailed by \citet{pourbaix2004}.

% Properties of barium stars.

Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases. The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr. In contrast, metal rich, young observable stars reaching the upper limit may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.

@@

Many barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}. Both studies show that the stellar populations of Barium stars can be separated into two groups when considering their \todo{absolute?} luminosity, kinematic, and spatial properties. Barium stars populating the halo have already been investigated \citep[e.g.][]{junqueira2001,drake2008,pereira2009,allen2006} and their relationship with metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}. Additionally, \citet{pereira2011} concludes metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. Furthermore, it is necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations   \citep{han1995}, explore the binary fraction at different metallicities, and infer AGB star yields at different masses and metallicities.

In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 273 Barium star candidates that show enhancements of s-process elements. In Section \ref{sec:observations} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign. In Section \ref{sec:discussion} we discuss the properties of our Barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:conclusion}

%and investigate atmospheric parameters including, the distributions of temperature, surface gravity and metalicity. Additionally, the abundances of elements not produced in the s-process such as sodium and technetium (Na and Tc) are examined to determine  if the sample Barium stars share similar abundance to field giants with equal metallicities. Moreover, the stellar sample is cross matched with GAIA, producing (not sure exactly what gaia gave us) neccessary to determine the kinematics of our Barium samples.

% move to observations and target selection:
%In our research we analysed 273 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 273 canidates.

\todo{move or remove: The red giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA\ and 4077\AA, respectively. (thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?). }
